---
title: Ženščina Dagestana OCRed files collection
output: 
  html_document:
    include:
      after_body: footer.html
knit: (function(inputFile, encoding) { 
      out_dir <- 'docs';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'index.html')) })
editor_options: 
  chunk_output_type: console
---

In this table the product of tesseract OCR engine applied to the collection of PDFs of the "Woman of Dagestan" magazine. See details about the project and implemented tools [in the github repository](https://github.com/LingConLab/zhenshchina_dagestana_magazine_parallel_corpus). At the moment, the page works very slowly but it works. Filtering options are disabled. Texts in languages with the "palochka" sign are recognised poorly sometimes.

With the corresponding buttons below you can copy to clipboard and export to .csv or .xlsx the table.



```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
library(tidyverse)
library(DT)
db <- read_csv('parallel_texts_table.csv')
```

```{r}
db %>% 
  datatable(#filter = 'top',
            extensions = 'Buttons',
            #plugins = "accent-neutralise",
            rownames = F,
            options = list(pageLength = 10, 
                           dom = 'Btip',
                           buttons = c('copy','csv','excel')
                           ))
```

