---
title: Ženščina Dagestana OCRed files collection
output: 
  html_document:
    include:
      after_body: footer.html
knit: (function(inputFile, encoding) { 
      out_dir <- 'docs';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'index.html')) })
editor_options: 
  chunk_output_type: console
---

In this table the product of tesseract OCR util applied to the collection of PDFs of the "Woman of Dagestan" magazine. See details about the project and implemented tools [in the github repository](https://github.com/LingConLab/zhenshchina_dagestana_magazine_parallel_corpus).

With the corresponding buttons below you can copy to clipboard and export to csv or excel currently filtered table.

Known issues:

- The table is large. At the moment, it loads *SLOWLY, BUT IT WORKS*, be patient, please.

- There is no palochka in the OCR model, thus texts on languages with this sign in the inventory are looking weird.

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
library(tidyverse)
library(DT)
db <- read_csv('parallel_texts_table.csv')
```

```{r}
db %>% 
  datatable(filter = 'top',
            extensions = 'Buttons',
            plugins = "accent-neutralise", # works with BOTH "comibining acute accent" with cyrillic and combining macron
            rownames = F,
            options = list(pageLength = 10, 
                           dom = 'Btip',
                           buttons = c('copy','csv','excel')
                           ))
```

